Intelligent Building Energy Management System

### 2021-05-08 finalReportPres.tex
Added files for presentation
Removed filed, updated flie paths

\begin{frame}{Agent and Web Server Communication}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.5]{figs/pubSubAgents.pdf}
        \caption{Publish Subscribe Model}
        \label{fig:pubSubModel}
    \end{figure}
    \begin{itemize}
        \item Agents and web server use the ZeroMQ
        messaging library
        \item Python wrapper used
    \end{itemize}
\end{frame}

@@

\begin{frame}{Embedded/Robotics Computer}{} % Elliot
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/notConnectedSBC.jpg}
            \caption{Embedded Computer Not Connected}
            \label{fig:not_connected_bb}
        \end{figure}

        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/connectedSBC.jpg}
            \caption{Embedded Computer Connected}
            \label{fig:connected_bb}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Embedded computer accepts control commands and sends data to the server
            \item Red LED indicates the embedded computer is not connected and green LED indicates the embedded computer is connected
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{WeMo Insight Switch}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \centering
        \includegraphics[scale=0.045]{figs/wemoView.jpg}
        \caption{WeMo Insight Smart Plug}
        \label{fig:wemo}
      \end{figure}
    \column{0.4\textwidth}
     \begin{block}{}
        \begin{itemize}
            \item Appliance is plugged into the WeMo Switch
            \item WeMo Switch can internally turn power on and off
            \item iBEMS will control the WeMo Switch remotely
        \end{itemize}
     \end{block}
    \end{columns}
\end{frame}

@@

\begin{frame}{Control Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/periodicQueryBehaviorFlow.pdf}
        \caption{periodicQueryBehavior Flow Chart}
        \label{fig:periodicQueryBehavior}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/setDeviceToActiveFlow.pdf}
        \caption{setDeviceToActive Flow Chart}
        \label{fig:setDeviceToActive}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/searchForDevicesFlow.pdf}
        \caption{searchForDevices Flow Chart}
        \label{fig:searchForDevices}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.30]{figs/Beaglebone_Receiver_Diagram.pdf}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Startup Menu}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.2]{figs/BEMS_GUI_Linux.png}
            \caption{Desktop GUI}
            \label{fig:desktopgui}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.35]{figs/BEMS_GUI_Linux_Warning.png}
            \caption{Popup Error}
            \label{fig:popuperror}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{itemize}
        \item Clicking "Start iBEMS" will lauch the web server and all 3 agents as well as launch the computer's web browser and load the login page automatically
        \item If the user accidentally clicks "Start iBEMS" while it already running, a warning message will appear to prevent errors
        \item Clicking "Stop iBEMS" will stop the web server and agents and close the web browser
    \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Startup Menu Functions}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/GUI_Diagram.pdf}
        \caption{Diagram for Startup Menu Functionality}
        \label{fig:GUI_Diagram}
    \end{figure}
\end{frame}

% System Architecture Diagram
\begin{frame}{Home Page}{} % Brian
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.2]{figs/Home_screen.png}
        \caption{Home Screen}
        \label{fig:Home_screen}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item This will be loaded when iBEMS is first booted and it simply shows some current data about the weather 
        \item The Home Page is also accessible by clicking the Home Icon in the upper left corner
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{Active Devices Page}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.13]{figs/ActiveDevices_screen.png}
            \caption{Active Devices Page}
            \label{fig:active_devices}
        \end{figure}
    \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Page allows users to directly control available devices in real time
            \item WeMo Insight Smart Plug can be turned on and off
            \item PWM duty cycle of the embedded computer can be adjusted in increments of 0.1
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}

\begin{frame}{WeMo Power Plot}{} % Brian
    \begin{figure}
        \centering
        \includegraphics[scale=0.15]{figs/ActiveDevices_plot.png}
        \caption{Active Devices Plot}
        \label{fig:active_devices_plot}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Clicking "View Status Plots" launches modal
            \item User can select any day and view the power usage
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

@@

    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.15]{figs/Applications_screen.png}
            \caption{Scheduling Page}
            \label{fig:schedulingl}
        \end{figure}
        \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Clicking on "Applications" on the nav bar loads the weekly scheduling feature
            \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}

>>>>

% \begin{frame}{Agent and Web Server Communication}{}
%     \begin{figure}
%         \centering
%         \includegraphics[scale=0.5]{figs/pubSubAgents.pdf}
%         \caption{Publish Subscribe Model}
%         \label{fig:pubSubModel}
%     \end{figure}
%     \begin{itemize}
%         \item Agents and web server use the ZeroMQ
%         messaging library
%         \item Python wrapper used
%     \end{itemize}
% \end{frame}

@@

\begin{frame}{Embedded/Robotics Computer}{} % Elliot
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/beaglebone/notConnectedSBC.jpg}
            \caption{Embedded Computer Not Connected}
            \label{fig:not_connected_bb}
        \end{figure}

        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/beaglebone/connectedSBC.jpg}
            \caption{Embedded Computer Connected}
            \label{fig:connected_bb}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Embedded computer accepts control commands and sends data to the server
            \item Red LED indicates the embedded computer is not connected and green LED indicates the embedded computer is connected
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{WeMo Insight Switch}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \centering
        \includegraphics[scale=0.045]{figs/wemo/wemoView.jpg}
        \caption{WeMo Insight Smart Plug}
        \label{fig:wemo}
      \end{figure}
    \column{0.4\textwidth}
     \begin{block}{}
        \begin{itemize}
            \item Appliance is plugged into the WeMo Switch
            \item WeMo Switch can internally turn power on and off
            \item iBEMS will control the WeMo Switch remotely
        \end{itemize}
     \end{block}
    \end{columns}
\end{frame}

@@

\begin{frame}{Control Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/agents/periodicQueryBehaviorFlow.pdf}
        \caption{periodicQueryBehavior Flow Chart}
        \label{fig:periodicQueryBehavior}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/agents/setDeviceToActiveFlow.pdf}
        \caption{setDeviceToActive Flow Chart}
        \label{fig:setDeviceToActive}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/agents/searchForDevicesFlow.pdf}
        \caption{searchForDevices Flow Chart}
        \label{fig:searchForDevices}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.30]{figs/beaglebone/Beaglebone_Receiver_Diagram.pdf}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Startup Menu}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.2]{figs/GUI/BEMS_GUI_Linux.png}
            \caption{Desktop GUI}
            \label{fig:desktopgui}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.35]{figs/GUI/BEMS_GUI_Linux_Warning.png}
            \caption{Popup Error}
            \label{fig:popuperror}
        \end{figure}
    \end{multicols}
    \begin{block}{}
      \begin{itemize}
        \item Clicking "Start iBEMS" will lauch the web server and all 3 agents as well as launch the computer's web browser and load the login page automatically
        \item If the user accidentally clicks "Start iBEMS" while it already running, a warning message will appear to prevent errors
        \item Clicking "Stop iBEMS" will stop the web server and agents and close the web browser
    \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Startup Menu Functions}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/GUI/GUI_Diagram.pdf}
        \caption{Diagram for Startup Menu Functionality}
        \label{fig:GUI_Diagram}
    \end{figure}
\end{frame}

% System Architecture Diagram
\begin{frame}{Home Page}{} % Brian
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.2]{figs/webServer/Home_screen.png}
        \caption{Home Screen}
        \label{fig:Home_screen}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item This will be loaded when iBEMS is first booted and it simply shows some current data about the weather 
        \item The Home Page is also accessible by clicking the Home Icon in the upper left corner
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

\begin{frame}{Active Devices Page}{} % Elliot 
    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.13]{figs/webServer/ActiveDevices_screen.png}
            \caption{Active Devices Page}
            \label{fig:active_devices}
        \end{figure}
    \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Page allows users to directly control available devices in real time
            \item WeMo Insight Smart Plug can be turned on and off
            \item PWM duty cycle of the embedded computer can be adjusted in increments of 0.1
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}

\begin{frame}{WeMo Power Plot}{} % Brian
    \begin{figure}
        \centering
        \includegraphics[scale=0.15]{figs/webServer/ActiveDevices_plot.png}
        \caption{Active Devices Plot}
        \label{fig:active_devices_plot}
    \end{figure}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
            \item Clicking "View Status Plots" launches modal
            \item User can select any day and view the power usage
        \end{itemize}
      \end{small}
    \end{block}
\end{frame}

@@

    \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
            \centering
            \includegraphics[scale=0.15]{figs/webServer/Applications_screen.png}
            \caption{Scheduling Page}
            \label{fig:schedulingl}
        \end{figure}
        \column{0.45\textwidth}
        \begin{block}{}
          \begin{itemize}
            \item Clicking on "Device Scheduling" on the nav bar loads the weekly scheduling feature
            \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)
        \end{itemize}
        \end{block}
    \end{columns}
\end{frame}
